Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-07 paper/ms.tex
Fix various minor things.

So far the strongest evidence for accretion of planetary material by a host
star comes from spectral analysis of polluted white dwarfs (WDs).
Because the gravitational settling times of elements heavier than \elem{He} in
atmosphere is much shorter than the WD cooling time, detection of metals likely
indicates the presence of a reservoir of dusty material around the WD.
Indeed, many of the polluted WDs host a dusty debris disk detected
in the infrared.
Some of the most dramatically polluted WDs show
surface abundances closely matched by rocky planetary material
with, e.g., bulk Earth composition, strongly arguing
that the disk formed from tidally disrupted minor planets
(\citealt{Zuckerman:2007aa,Klein:2010aa}).
Recently, transit signals from small bodies orbiting around a polluted WD
has been detected by \project{Kepler} adding further support to the picture
(\citealt{2015Natur.526..546V}).

@@

Throughout the \documentname\, we use the following convention for
chemical abundances of stars: [\elemH{X}] is the ratio of number density of
element \elem{X} to \elem{H} relative to the solar values.
The absolute abundance of \elem{X} is
$A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
where $n_\elem{X}$ is the number density of element \elem{X}.

@@

Anticipating the forth coming discussion, we review and summarize a handful of
wide binary systems that have been studied in
their detailed chemical abundances so far with high-resolution spectroscopy.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We focus on key characteristics of stars and planets, and interpretation of any
trend in $\Delta\elemH{X}$ with \Tcondens.
%TODO: needs to include **16 Cyg** and HD~133131AB

{\bf HD~20782/HD~20782:}
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2\arcmin\ sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.

>>>>

So far the strongest evidence for accretion of planetary material by a host
star comes from spectral analysis of polluted white dwarfs (WDs).
Because the gravitational settling times of elements heavier than \elem{He} in
atmosphere is much shorter than the WD cooling time, detection of metals likely
indicates the presence of a reservoir of dusty material around the WD.
Indeed, many of the polluted WDs host a dusty debris disk detected
in the infrared.
Some of the most dramatically polluted WDs show
surface abundances closely matched by rocky planetary material
with, e.g., bulk Earth composition, strongly arguing
that the disk formed from tidally disrupted minor planets
(\citealt{Zuckerman:2007aa,Klein:2010aa}).
Recently, transit signals from small bodies orbiting around a polluted WD
have been detected by \project{Kepler} adding further support to the picture
(\citealt{2015Natur.526..546V}).

@@

Throughout the \documentname\, we use the following convention for
chemical abundances of stars: \elemH{X} is the ratio of number density of
element \elem{X} to \elem{H} relative to the solar value.
The absolute abundance of \elem{X} is
$A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
where $n_\elem{X}$ is the number density of element \elem{X}.

@@

Anticipating the forthcoming discussion, we review and summarize a handful of
wide binary systems that have been studied in
their detailed chemical abundances so far with high-resolution spectroscopy.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We focus on key characteristics of stars and planets, and interpretations of
any trend in $\Delta\elemH{X}$ with \Tcondens.
%TODO: needs to include **16 Cyg** and HD~133131AB

{\bf HD~20782/HD~20781:}
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2\arcmin\ sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.
